\speculake: Hiding Malware in Speculative Execution

### 2018-08-07 paper/triggers.tex
add paragraph about trigger inputs to intro
added implementation section for spectre 1.1
fix citation

We observe that communication could also go in the other direction: from
the payload program back to the remote adversary, also via the benign application
intermediary. The payload program could influence the performance of the benign
application, and the adversary could time responses from the benign application
to receive covert information from the malicious payload~\cite{netspectre}. This would allow the
malicious payload to operate \emph{entirely speculatively}, without assistance
from the real world for keeping state.

@@

\subsection{Speculative Buffer Overflow}

\FigSpectreOne

>>>>

We observe that communication could also go in the other direction: from the
payload program back to the remote adversary, also via the benign application
intermediary. The payload program could influence the performance of the benign
application, and the adversary could time responses from the benign application
to receive covert information from the malicious
payload~\cite{schwarz2018netspectre}. This would allow the malicious payload to
operate \emph{entirely speculatively}, without assistance from the real world
for keeping state.

@@

\subsection{Speculative Buffer Overflow}
\label{subsec:spec-buffer-overflow}
